Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-06-14 paper/paper.tex
Consistency

\documentclass{llncs}
\usepackage[pass,showframe]{geometry}

@@

    \caption{Cumulative performance.}

@@

    \caption{Per-instance speedups for unlabelled, undirected graphs.}
\end{figure}

@@

    \caption{Scalability and reproducibility, clique algorithm}
\end{figure}

@@

    \caption{Scalability and reproducibility, McSplit algorithm}
\end{figure}

>>>>

\documentclass{llncs}
\usepackage[pass]{geometry}

@@

    \caption{Cumulative performance. The parallel versions, dotted, are always better in aggregate
    than the sequential versions, solid.}

@@

    \caption{Per-instance speedups for unlabelled, undirected graphs. The histograms show the
    distribution of speedups for instances whose sequential runtime is at least $50$ milliseconds
    and no more than $100$ seconds (and so they under-represent superlinear speedups slightly).}
\end{figure}

@@

    \caption{Scalability and reproducibility, clique algorithm.}
\end{figure}

@@

    \caption{Scalability and reproducibility, McSplit algorithm.}
\end{figure}
